GSE158422: DNA methylation in Lung squamous cell carcinoma - gene methylation enrichment analysis

### 2023-10-01 figs/GSE158422_split.Rmd
tidy up results

  # la2
  dm2 <- runlimma(mval_b,design_b,myann)
  dmagg2 <- agg(dm2,cores=CORES)
  m2 <- dmagg2$gme_res_df[,"mean",drop=FALSE]
  lares2 <- ttenrich(m=m2,genesets=gs_symbols,cores=CORES)
}

@@

laout <- do.call(rbind,lapply(lares,lacompare))

>>>>

  # la2
  dm2 <- runlimma(mval_b,design_b,myann)
  dmagg2 <- agg(dm2,cores=CORES)
  m2 <- dmagg2$gme_res_df[,"mean",drop=FALSE]
  lares2 <- ttenrich(m=m2,genesets=gs_symbols,cores=CORES)

  list("lares1"=lares1,"lares2"=lares2)

}

@@

laout <- lapply(lares,lacompare)
laout <- do.call(rbind,lapply(lares,lacompare))
